\documentclass[12pt,a4paper]{article}
\usepackage[a4paper,margin=1.5cm]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{parskip}
\pagestyle{empty}
\usepackage{unicode-math}

\setmainfont{Carlito}

\definecolor{primary}{HTML}{1a1a1a}

\titleformat{\section}{\color{primary}\scshape\large\raggedright}{}{0em}{}[\titlerule]
\titleformat{\subsection}[runin]{\bfseries}{}{0em}{}[ -- ]

\newcommand{\name}[1]{\textbf{\Huge #1}}
\newcommand{\contact}[4]{
  #1 \enskip | \enskip \href{mailto:#2}{#2} \enskip | \enskip #3 \enskip | \enskip \href{https://#4}{#4}
}
\newcommand{\cvitem}[2]{
  \noindent\textbf{#1} \hfill #2\\
}
\newcommand{\cvsubitem}[2]{
  \noindent#1 \hfill \textit{#2}\\
}
\newcommand{\bulletlist}[1]{
  \begin{itemize}[leftmargin=*]
    #1
  \end{itemize}
}
\newcommand{\cvcertification}[3]{
  \noindent\textbf{#1} \hfill #2\\Credential ID: #3\\
}

% ------------------------------------------------------------------------------------------------

\begin{document}
\name{Tiago Caetano Henriques da Costa}\\
\contact {Lisboa, Portugal}{tiagoccosta@proton.me}{+351 111 222 333}{digitalillusion.pt}

\vspace{0.5cm}

Senior DevOps/Platform Engineer with 10+ years of experience designing, building, and scaling cloud-
native platforms and internal tooling. Strong background in Kubernetes-based architectures, CI/CD
automation, infrastructure as code, and secure-by-default cloud solutions. Passionate about developer
experience, system reliability, and building reusable platform capabilities that enable engineering
teams to ship faster and more safely.

% ------------------------------------------------------------------------------------------------

\section*{Professional Experience}

\cvitem{CGI Inc.}{Nov 2017 -- Present}  
\textit{Senior DevOps/Software Engineer}

\bulletlist{
  \item Designed, built, and scaled cloud-native infrastructure supporting microservices platforms for enterprise clients. 
  \item Implemented and maintained 70+ reusable CI/CD pipelines using Azure DevOps YAML, improving deployment consistency and developer autonomy.
  \item Led containerization and orchestration initiatives using Docker and Azure Kubernetes Service (AKS).
  \item Built internal automation tooling for secret rotation, vulnerability scanning, integration testing, and release governance among others.
  \item Applied infrastructure-as-code practices to ensure repeatable, auditable, and secure platform changes.
  \item Supported incident response activities and contributed to post-incident improvements to platform reliability and resilience.
  \item Assisted new team members through mentorship, providing technical guidance and sharing knowledge of the system.
}

\cvitem{IsGreen LDA}{Abr 2014 -- Oct 2017}
\textit{Software Engineer}

\bulletlist{
  \item Designed and implemented an IoT platform for intelligent building lighting management, including gateways and sensor devices.
  \item Built internal backoffice systems and analytics dashboards to support large-scale IoT data ingestion.
  \item Administered Linux servers, databases, and internal networks.
}

% ------------------------------------------------------------------------------------------------

\section*{Education}

\cvitem{Bachelor in Computer Engineering}{}  
\textit{Instituto Superior de Engenharia de Lisboa}

\section*{Technical Skills}
\textbf{DevOps \& Infrastructure:} Azure DevOps, Docker, Kubernetes, Git \\
\textbf{Cloud Platforms:} Microsoft Azure \\
\textbf{Programming \& Scripting:} C\#, Powershell, YAML, Bash, Java, JavaScript \\
\textbf{Frameworks:} .NET, Angular, Entity Framework, ASP.Net


\section*{Certifications}
\cvcertification{Certified Kubernetes Application Developer (CKAD)}{}{LF-yqhy1b31p9}
\cvcertification{Microsoft Certified: DevOps Engineer Expert (AZ-400)}{}{CE338525F66C4F9A}
\cvcertification{Microsoft Certified: Azure Developer Associate (AZ-204)}{}{87D94EE16B9ECB26}
\cvcertification{Microsoft Certified: Azure Fundamentals (AZ-900)}{}{E8FF22C47B2CA235}

% ------------------------------------------------------------------------------------------------

\end{document}
