%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Senior Developer}
{CGI}
{Lisbon, Portugal}
{Nov. 2017 - Present}
{
    \begin{cvitems}
        \item {Responsible for all DevOps procedures required to support an Azure cloud solution implemented mainly using microservices}
        \begin{itemize}
            \item {Development and maintenance of current and new pipelines}
            \item {Release management for code and builds to several environments using CI/CD practises}
            \item {Automation of various internal procedures (e.g. vulnerability scanning of containers, report generation for unit and BDD tests)}
        \end{itemize}
        \item {Migration of a utilities company's legacy backend services and databases (Oracle based) to Microsoft Azure cloud}
        \begin{itemize}
            \item {Reports migration from Oracle Report Builder to Microsoft PowerBI}
            \item {Database migration from Oracle Database to Azure SQL Database}
            \item {Migrate CDC processes from Oracle CDC to Qlik}
        \end{itemize}
        \item {Development of backend services for a mobile app that provides end-to-end fully encrypted messaging and payment service for businesses and consumers using Microsoft technologies.}
        \item {Development of a new system using Microsoft Azure technologies with the aim of replacing the current system for an utilities company}
        \begin{itemize}
            \item {Backend microservices for transformation and processing of balancing data received from electricity generators and suppliers}
            \item {This project involved working for 4 months in the UK as an expatriate.}
        \end{itemize}
        \item {Development of a subscription project to carry out health and welfare studies with the following components:}
        \begin{itemize}
            \item {Web portal for creating health and welfare studies.}
            \item {Backend services for management of the study data, including data validation and persistance into a database}
        \end{itemize}
    \end{cvitems}
}

\cventry
{Software Engineer } % Job title
{IsGreen LDA} % Organization
{Lisbon, Portugal} % Location
{Apr. 2014 - Oct. 2017} % Date(s)
{ % Description(s) of tasks/responsibilities
    \begin{cvitems}
        \item {Implemented a complete IoT plataform for intelligent light management in buildings (inc. gateway and devices).}
        \item {Implemented a backoffice for client management and data collection and analysis.}
        \item {Implemented an Android aplication for receiving event notifications sent by the IoT plataform.}
        \item {Network and database administration.}
        \item {Domain management.}
    \end{cvitems}
}

\end{cventries}